Bayesian multivariate skew-normal finite mixture model for analysis of infant development trajectories

### 2019-06-04 manuscript/manuscript.tex
approaches

A ubiquitous feature of repeated measures studies is loss of data due to intermittent missingness and attrition. In the Bayesian setting, the standard approach to dealing with missing data is to perform multiple imputation, whereby $m$ imputed data sets are generated from a specified imputation model. After $m$ complete data sets are obtained, parameter estimates are combined across each data set to produce a final set of parameter estimates (Gelman \textit{et al.} 2013). This approach is not only computationally burdensome, requiring storage and analysis of an $m \times n_{rows} \times n_{cols}$ data array in addition to multiplication of total model run time by a factor of $m$, but it has been shown to produce unreliable inferences (Zhou and Reiter, 2010). We instead

>>>>

\textbf{\textit{Put lit review of Bayesian multinomial logistic regression here}}

A ubiquitous feature of repeated measures studies is loss of data due to intermittent missingness and attrition. In the Bayesian setting, the standard approach to dealing with missing data is to perform multiple imputation, whereby $m$ imputed data sets are generated from a specified imputation model. After $m$ complete data sets are obtained, parameter estimates are combined across each data set to produce a final set of parameter estimates (Gelman \textit{et al.} 2013). This approach is not only computationally burdensome, requiring storage and analysis of an $m \times n_{rows} \times n_{cols}$ data array in addition to multiplication of total model run time by a factor of $m$, but it has been shown to produce unreliable inferences (Zhou and Reiter, 2010). We instead include an ``online" imputation imputation step in our Gibbs sampling procedure, whereby missing outcomes are updated at each iteration. This approach greatly increases the number of opportunities for exploration of the missing data parameter space.
